---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# JSmediation

[![CRAN status](https://www.r-pkg.org/badges/version/JSmediation)](https://cran.r-project.org/package=JSmediation) [![Travis build status](https://travis-ci.org/cedricbatailler/JSmediation.svg?branch=master)](https://travis-ci.org/cedricbatailler/JSmediation)

`JSmediation` is an R package aiming to provide a set of functions to conduct a 
joint-significance test in a context of mediation analysis. Note that 
`JSmediation` is still under active development.

## Scope

The goal of `JSmediation` is to provide a consistent syntax to conduct 
joint-significance tests. To do so, it provides a family of `mdt_*`
functions helping one conducting different mediation analysis.

Current implemented models are:

- simple mediation (`mdt_simple`)
- within-participant mediation (`mdt_within`, but see also `mdt_within_w`)
- moderated mediation (`mdt_moderated`)

Every `mdt_*` functions take at least four arguments: `data` (the data frame 
containing the data to be used),` IV` (the unquoted column name of the independent variable in the data frame), `DV` (the unquoted column name of the 
dependent variable in the data frame), and `M` (the unquoted column name of the
mediator in the data frame).

## Installation

<!--
You can install the released version of JSmediation from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("JSmediation")
```
-->
You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("cedricbatailler/JSmediation", build_vignettes = TRUE)
```



## How to use JSmediation

```{r}
library(JSmediation)
```

The `JSmediation` package contains several functions as well as example data 
sets that can be used as an example. The `ho_et_al` data set comes from 
Ho et al. (2017; Exp. 3) and contains variables to test a simple mediation. As a
simple example, we will conduct a joint-significance test of the indirect effect
of discrimination on hypodescent passing by linked fate. 

We will first recode `condition` variable which is a character to a contrast 
code using the `build_contrast` function.

```{r}
data("ho_et_al")

ho_et_al$condition_c <- build_contrast(ho_et_al$condition, 
                                       "High discrimination",
                                       "Low discrimination")

head(ho_et_al)
```

Now, we can conduct a joint significant test using the `mdt_simple` function.

```{r}
JS_model <- mdt_simple(ho_et_al, 
                       DV = hypodescent, 
                       IV = condition_c, 
                       M  = linkedfate)

JS_model
```

One will have to make sure that both $a$ and $b$ are significant to conclude 
that there is a mediation pattern.

### References

Ho, A. K., Kteily, N. S., & Chen, J. M. (2017). “You’re one of us”: Black 
Americans’ use of hypodescent and its association with egalitarianism. 
_Journal of Personality and Social Psychology_, _113_(5), 753‑768. doi:
10.1037/pspi0000107

## Contributing
Contributions are absolutly welcome. Please note that this project is released 
with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).

By participating in this project you agree to abide by its terms.
