---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# JSmediation

[![Travis build status](https://travis-ci.org/cedricbatailler/JSmediation.svg?branch=master)](https://travis-ci.org/cedricbatailler/JSmediation)

The goal of `JSmediation` is to provide a set of functions to conduct a 
joint-significant test in a context of moderation analysis. Note that 
`JSmediation` is still under active developement.


## Installation

<!--
You can install the released version of JSmediation from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("JSmediation")
```
-->
You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("cedricbatailler/JSmediation")
```

## How to use JSmediation

```{r}
library(JSmediation)
```

The `JSmediation` package contains several functions as well as an example data 
set (`ho_et_al`) that can be used as an example. This data set comes from 
Ho et al. (2017; Exp. 3) and contains variables to test a simple mediation. As a
simple example, we will conduct a joint-significance test of the indirect effect
of discrimination on hypodescent passing by linked fate. 

We will first recode `condition` variable which is a character to a contrast 
code using the `build_contrast` function.

```{r}
data("ho_et_al")

ho_et_al$condition_c <- build_contrast(ho_et_al$condition, 
                                       "High discrimination",
                                       "Low discrimination")

head(ho_et_al)
```

Now, we can conduct a joint significant test using the `mdt_simple` function.

```{r}
JS_model <- mdt_simple(ho_et_al, 
                       DV = hypodescent, 
                       IV = condition_c, 
                       M  = linkedfate)

JS_model
```



## References

Ho, A. K., Kteily, N. S., & Chen, J. M. (2017). “You’re one of us”: Black 
Americans’ use of hypodescent and its association with egalitarianism. 
_Journal of Personality and Social Psychology_, _113_(5), 753‑768. doi:
10.1037/pspi0000107
