---
title: "mediation analysis with JSmediation"
author: "Cédric Batailler"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mediation analysis with JSmediation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Fit a simple mediation analysis
## Joint Significance approach
$$ \hat{Y_i} = \beta_0 + \beta_1 X_i$$ 
$$ \hat{M_i} = \beta_0 + \beta_1 X_i$$ 
$$ \hat{Y_i} = \beta_0 + \beta_1 X_i + \beta_2 M_i$$ 

## R implementation

`JSmediation` offers helpers to use Joint Significance approach.  With this 
package, you can type a mediation model the way you think it, `JSmediation` 
dealing with fitting underlying models.

```{r}
library(JSmediation)
```

```{r}
head(linkedfate)
```

```{r}
linkedfate$condition_c <- build_contrast(linkedfate$condition,
                                         "Low discrimination",
                                         "High discrimination")
```



```{r}
my_model <- mdt_simple(linkedfate,
                       IV = condition_c,
                       DV = hypodescent,
                       M  = linked_fate)
```

```{r}
my_model
```
## Confidence interval

```{r}
add_ci(my_model)
```

# Helper functions

## Building a contrast code

## Extracting individual models
